Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-29 paper/main.tex
on compile time

Tables~\ref{tab:table_cpp1}-\ref{tab:table_rust1} compare generated
mutants for ``Regex'' and ``Comby'' modes of our tool.  Invalid
mutants are mutants that the tool produces, but which fail to
compile.  The cost of each such mutant is usually small,
since compilation generally fails early for trivial reasons (e.g.,
{\tt break} or {\tt continue} outside a loop), 
but reducing the number of such mutants directly reduces the cost of
initial mutant generation, and generally indicates a better
``understanding'' of the source being mutated.
\clg{What are LOC in the tables?}

@@

We do not report the time taken for mutation generation and testing,
since due to only Dextools using schema (and PIT using bytecode mutants), most tools took similar
amounts of time to compile mutants, and mutant execution time was
generally similar, except for tools that produced very few mutants.
We expect that our approach is generally slower for initial mutant
generation, due to a higher number of invalid mutants, but that this
cost is relatively small compared to the time required to compile and
execute valid mutants for almost all projects.

>>>>

Tables~\ref{tab:table_cpp1}-\ref{tab:table_rust1} compare generated
mutants for ``Regex'' and ``Comby'' modes of our tool.  Invalid
mutants are mutants that the tool produces, but which fail to
compile.  The cost of each such mutant is usually small,
since compilation generally fails early for trivial reasons (e.g.,
{\tt break} or {\tt continue} outside a loop), 
but reducing the number of such mutants directly reduces the cost of
initial mutant generation, and generally indicates a better
``understanding'' of the source being mutated.

@@

We do not report the time taken for mutation generation and testing,
since due to only Dextools using schema (and PIT using bytecode mutants), most tools took similar
amounts of time to compile mutants, and mutant execution time was
generally similar, except for tools that produced very few mutants.
We expect that our approach is generally slower for initial mutant
generation, due to a higher number of invalid mutants, but that this
cost is relatively small compared to the time required to compile and
execute valid mutants for almost all projects.  An informal study of
large Java projects by the author of the PIT gradle
plugin\footnote{\url{https://solidsoft.wordpress.com/2017/09/19/how-fast-or-slow-mutation-testing-really-is/}}
  suggests that even a successful compile of a typical project takes
  somewhere between one-sixth to one-third the time required for
  executing tests, and failed compiles are usually much
  faster than successful ones.
